ComBatLS Replication Results

### 2024-08-16 paper_replication_results.Rmd
remove deprecated scripts

1. `ukb_curation-eda.Rmd`
2. `run_permutation_pipeline.sh`
   - `R_scripts/permute_sites_.R`
   - `R_scripts/combat_apply.R`
   - `R_scripts/fit_perm_basic_mod.R`
   - `R_scripts/fit_centiles.R`
   - `R_scripts/summarise_cent_subj-wise.R`
3. `run_permutation_stats.sh`
   - `R_scripts/summarise_cent_subj-wise.R`
   - `R_scripts/ratio_results.R`
   - `R_scripts/featurewise_sex_bias_test.R`
   - `R_scripts/remove_extremes_single.R`
4. `pull_stats.sh`

>>>>

1. `ukb_curation-eda.Rmd`
2. `run_permutation_pipeline.sh`
   - `R_scripts/permute_sites.R`
   - `R_scripts/combat_apply.R`
   - `R_scripts/fit_perm_basic_mod.R`
   - `R_scripts/fit_centiles.R`
   - `R_scripts/summarise_cent_subj-wise.R`
3. `run_permutation_stats.sh`
   - `R_scripts/summarise_cent_subj-wise.R`
   - `R_scripts/ratio_results.R`
   - `R_scripts/featurewise_sex_bias_test.R`
   - `R_scripts/remove_extremes_single.R`
4. `pull_stats.sh`
